\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables


% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
  Paso, Texas USA} 
\acmYear{1997}
\copyrightyear{2016}

\acmPrice{15.00}


\begin{document}
\title{A Portable Load Balancer for Kubernetes Cluster}
\titlenote{Produces the permission block, and
  copyright information}
\subtitle{Extended Abstract}
\subtitlenote{The full version of the author's guide is available as
  \texttt{acmart.pdf} document}


\author{Kimitoshi Takahashi}
\authornote{Dr.~Trovato insisted his name be first.}
\orcid{/0000-0001-5774-6725}
\affiliation{%
  \institution{The Graduate University for Advanced Studies}
  \streetaddress{2-1-2 Hitotsubashi}
  \city{Chiyoda-ku}
  \state{Tokyo} 
  \postcode{101-8430}
  \country{Japan}
}
\email{ktaka@nii.ac.jp}

\author{Kento Aida}
\authornote{The secretary disavows any knowledge of this author's actions.}
\affiliation{%
  \institution{National Institute of Informatics}
  \streetaddress{2-1-2 Hitotsubashi}
  \city{Chiyoda-ku}
  \state{Tokyo} 
  \postcode{101-8430}
  \country{Japan}
}
\email{aida@nii.ac.jp}

\author{Tomoya Tanjo}
\authornote{This author is the
  one who did all the really hard work.}
\affiliation{%
  \institution{National Institute of Informatics}
  \streetaddress{2-1-2 Hitotsubashi}
  \city{Chiyoda-ku}
  \state{Tokyo} 
  \postcode{101-8430}
  \country{Japan}
}
\email{tanjo@nii.ac.jp}

\author{Jingtao Sun}
\affiliation{%
  \institution{National Institute of Informatics}
  \streetaddress{2-1-2 Hitotsubashi}
  \city{Chiyoda-ku}
  \state{Tokyo} 
  \postcode{101-8430}
  \country{Japan}
}
\email{sun@nii.ac.jp}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{B. Trovato et al.}


\begin{abstract}
Recently Linux Containers are getting popular because of its lightweight nature.
WEB service applications are often deployed as cluster of a containers.

There are needs for those WEB services to be able to migrate to different cloud providers
or on-premise data centers, for BCP(Business continuity planning) or DR(Disaster Recovery) purposes.

The Kubernetes container management system is a prominet candidate to enable such container cluster migration.
However since the Kubernetes relies on external loadbalancer to route the traffic from the internet into some of the nodes where containers run on, 
it is not guaranteed to always work.
There are many load balancers which kubernetes does not support, 
especially if it is a hardware load balancer used in on-premise datacenters.

To overcome this paper investigate feasibility of a software load balancer deployed as a container run by the Kubernets. 
We will implement ipvs layer 4 load balancer as a container and discuss the feasibility of it by comparing the performances of such loadbalancers.

\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}


\keywords{ACM proceedings, \LaTeX, text tagging}


\maketitle

\input{body}

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography} 

\end{document}
